The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-02 Writeup/paper_v3.tex
MI explanation added

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on $K$-corrected $F814W$-band magnitudes, denoted as $M_I$.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
\rachel{Actually, is this the catalog entry called ``MI''?  If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
We plot their SMF for \emph{all} in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.

>>>>

COSMOS is a flux-limited survey and is therefore affected by Malmquist bias, i.e. at higher redshifts, the brighter galaxies are preferentially observed.
Our analysis involves comparing galaxies in different redshift slices to find significant differences in morphology, if any, so with a flux-limited sample, we would be comparing only the bright galaxies at high redshifts with
bright and faint galaxies at low redshifts. For a fair comparison, we must restrict ourselves to bright galaxies at all redshifts and this is acheived by volume-limiting the sample.
%\rachel{Explain why you are doing this.  Before saying {\em how} you
%  generate a volume-limited sample, explain {\em why} you are
%  generating one.}
We generate, using the method below, a volume-limited sample that is complete upto $z=1$ by applying a cut on luminosity such that only galaxies instrinsically brighter than a certain threshold is considered. This threshold is set on  $M_I$, which are $K$-corrected $i^+$-band magnitudes from Subaru or from the PSF-matched CHFT $i^*$-band images.
\rachel{Is it $i$ band, or $I$ band?  Check which one and then be
  self-consistent throughout the text.}\arun{I think they call it
  $I_{814}$, so $I$.}
\rachel{But you are still being ambiguous in sometimes calling it $I$
  and other times F814W.  Pick one.}
\rachel{Actually, is this the catalog entry called ``MI''?  If so, it really is a different band - it's the k-corrected $I$-band data from Suburu or CFHT, so it's appropriate to call it $M_I$ and explain briefly that it's from the Subaru data (but $m_{F814W}$, since MAG\_AUTO is from F814W).}
Since the parent sample contains fainter galaxies, upto $m_\text{F814W}=25.2$, we compare the distribution of the $m_\text{F814W}=23.5$ sample with the samples containing fainter galaxies for high redshift bins, to see where the sample is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}

@@

%Alternatively, we can impose cuts on stellar mass of the galaxies instead of imposing on the luminosity. 
%If we restrict to galaxies with masses $M$ such that $\log(M/M_\odot) \ge 10.15$, then we have at least {\bf 95.0\% } completeness.
Alternatively, one could get around the problem of considering redshift evolution by imposing cuts on stellar mass instead of absolute luminosity in a particular band. In Fig.~\ref{fig:smf}, we show the stellar mass function (SMF) of our sample for various F814W flux limit.
\cite{Tomczak_SMF} report the SMFs for the ZFOURGE survey, which includes COSMOS. They considered for this work, a single stellar population following a Chabrier IMF~\citep{ChabrierIMF}. 
We plot their SMF for \emph{all} galaxies in Fig.~\ref{fig:smf} for
reference. Their SMF is higher than ours since they reach $K_s$-band
$5\sigma$ depth of 24.9. 
As in the case of $M_I$ s, we compare the stellar mass in the $m_\text{F814W}\le23.5$ sample with that of the $m_\text{F814W}\le25.2$ sample. 
The sample $\log(M/M_\odot) > 10.15$ is about 95\% complete in the redshift bin $\left[ 0.75 - 0.85\right]$ and has 10,341 galaxies in total.
Thus, we construct a third volume-limited sample \s$3$ by imposing the stellar mass cut mentioned above. The number of galaxies in redshift slices
are tabulated in Table \ref{table:GalaxyCounts} for all 3 ways of obtaining a volume-limited sample. Stellar-mass limited sample happens to be the smallest one.
